Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-23 ms.tex
simplifying discussion.

The first two lines are a piecewise power law fit designed to
approximately reproduce the solid line in Figure 6 in
\citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
heats the electrons. For $\eddrt\gsim 0.1$, $\epsilon_{\rm rad}$
should saturate to 0.1, hence the fourth line. The third line is a
power law which connects $\epsilon_{\rm rad} (\eddrt=0.01) = 0.026$ to
$\epsilon_{\rm rad} (\eddrt=0.1) = 0.1$. The tildes are put in as a
reminder that the efficiency will depend on the small scale $\Mdot$
($\tilde{\dot{M}}$) which will in general be different from the large
scale $\Mdot$.

Additionally, a large fraction of the $\dot{M}$ on large scales will
be driven out in outflows as the gas has some non-zero angular
momentum and a centrifugal barrier will stop it from accreting
\citet{Li+2013}. In the limit weak cooling appropriate for low
accretion rates the accretion rate on small scales will be of order
$\alpha \Mdot$.  We take $\epsilon=\alpha \epsilon_{\rm rad}$ for the
overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
equation~\eqref{eq:efficiency}. This means that the bolometric
luminosity, $L=\epsilon \Mdot c^2=\alpha \epsilon_{\rm rad} (\alpha
\eddr) \Mdot c^2= \epsilon_{\rm rad} (\eddrt) \tilde{\dot{M}} c^2$, where
$\Mdot$ is mass inflow rate on large scales and $\tilde{\dot{M}}$ is
the mass inflow rate on small scales. Note that in evaluating the
efficiency one has to account for the $\alpha$ suppression in $\eddr$.
we obtain {\bf AG note the change in the description of the
  efficiency. Also, the alpha's kept tripping me up},

@@

\citet{BergerZauderer+:2012a} infer a flattening of the gas density
profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc
(their Fig.~6) which looks qualitatively similar to the shape density
profile we predict for core galaxies (Fig.~\ref{fig:profiles}, solid
line).  To obtain such a flattening on the inferred radial scales
would require a black hole of $\Mbh\sim 10^7 \Msun$.  However, this is
inconsistent with the break in the gas density seen at $\sim 0.6$ pc
by \citet{BergerZauderer+:2012a}, which should correspond to the break
radius of the {\it stellar density} profile, thus implying an
unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to
the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}. We
also note that other constraints (the observed jet power, the jet
shut-off (if linked with the accretion becoming sub-Eddington), and an
observed QPO in the x-ray light curve) favor a smaller black hole
($10^5-10^6 \Msun$) \citep{Tchekhovskoy+2014}.

Alternatively, the observed density break in J1644+57 could result
from the outer edge of a sub-parsec nuclear star cluster (e.g.,
\citealt{Carson+15}).  The high stellar densities of such a compact
star cluster could greatly enhance the TDE rate
(e.g.~\citealt{Stone&Metzger15}), possibly making this association
uncoincidental.

>>>>

The first two lines are a piecewise power law fit designed to
approximately reproduce the solid line in Figure 6 in
\citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
heats the electrons. We assume that $\epsilon_{\rm rad}$ saturates to
0.1 at $\eddrt\simeq 0.1$. $\tilde{\dot{M}}$ correspond to the true
accretion rate (as opposed to the inflow rate on large scales--which
is generally what we mean by $\Mdot$).

Additionally, a large fraction of the $\dot{M}$ on large scales will
be driven out in outflows as the gas has some non-zero angular
momentum and a centrifugal barrier will stop it from accreting
\citet{Li+2013}. In the limit weak cooling appropriate for low
accretion rates the accretion rate on small scales will be of order
$\alpha \Mdot$.  We take $\epsilon=\alpha \epsilon_{\rm rad}$ for the
overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
equation~\eqref{eq:efficiency}. Note that in evaluating the efficiency
one has to use $\tilde{\dot{M}}\simeq \alpha \Mdot$. 
% This means that the bolometric
% luminosity, $L=\epsilon \Mdot c^2=\alpha \epsilon_{\rm rad} (\alpha
% \eddr) \Mdot c^2= \epsilon_{\rm rad} (\eddrt) \tilde{\dot{M}} c^2$, where
% $\Mdot$ is mass inflow rate on large scales and $\tilde{\dot{M}}$ is
% the mass inflow rate on small scales. Note that in evaluating the
% efficiency one has to account for the $\alpha$ suppression in $\eddr$.
% we obtain 
{\bf AG note the change in the description of the
  efficiency. Also, the alpha's kept tripping me up},

@@

\citet{BergerZauderer+:2012a} infer a flattening of the gas density
profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc
(their Fig.~6) which looks qualitatively similar to the shape density
profile we predict for core galaxies (Fig.~\ref{fig:profiles}, solid
line).  To obtain such a flattening on the inferred radial scales
would require a black hole of $\Mbh\sim 10^7 \Msun$.  However, this is
inconsistent with the break in the gas density seen at $\sim 0.6$ pc
by \citet{BergerZauderer+:2012a}, which should correspond to the break
radius of the {\it stellar density} profile, thus implying an
unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to
the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.
Alternatively, the observed density break in J1644+57 could result
from the outer edge of a sub-parsec nuclear star cluster (e.g.,
\citealt{Carson+15}).  The high stellar densities of such a compact
star cluster could greatly enhance the TDE rate
(e.g.~\citealt{Stone&Metzger15}), possibly making this association
uncoincidental.

 We also note that \citet{Tchekhovskoy+2014} favor a smaller black hole
($10^5-10^6 \Msun$) for J1644+57 based on the observed jet power, the jet
shut-off time (if linked with the accretion becoming sub-Eddington), and an
observed QPO in the x-ray light curve favor a smaller black hole {\bf
  AG Gone mad!}.
